\documentclass[11pt,journal,compsoc]{IEEEtran}

\makeatletter
\renewcommand{\@IEEEsectpunct}{\ \,}% Modified from {:\ \,}
\makeatother

% *** GRAPHICS RELATED PACKAGES ***


% *** MATH PACKAGES ***
\usepackage[cmex10]{amsmath}
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does.



% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
\usepackage{float}
\usepackage{stfloats}
\usepackage{caption}
\captionsetup{
	font=scriptsize,
	labelfont=scriptsize,
}
\captionsetup[lstlisting]{justification=centering}


% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage[colorlinks]{hyperref}
\hypersetup{
 urlcolor = blue
}

% Correct bad hyphenation here
\hyphenation{}

%----------------------------------------------------------------------------------------
%	CONFIGURATION OF CODE LISTINGS
%----------------------------------------------------------------------------------------
\usepackage[font=scriptsize,labelfont=scriptsize]{subcaption}
\usepackage{listings}
\usepackage{color}
 
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
 
\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
}
 
\lstset{style=mystyle}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% OWN:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[
    backend=biber,
    url=true
]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{hyperref}	
\usepackage{todonotes}	

\usepackage{multirow}

\usepackage[english]{babel}

\begin{document}
%

\title{Politicians and Nobel Prizes}

\author{Katrien Laenen,
        Ward Schodts
        and~Gust Verbruggen\\ 
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem katrien.laenen@student.kuleuven.be
\IEEEcompsocthanksitem ward.schodts@student.kuleuven.be
\IEEEcompsocthanksitem gust.verbruggen@student.kuleuven.be}%

}

% The paper headers
\markboth{Knowledge \& the Web, 2015-2016}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}


% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}


\IEEEtitleabstractindextext{%
\begin{abstract}
In this paper we try to find the politicians which have a high change of receiving a Nobel Prize. 
\end{abstract}

\begin{IEEEkeywords}
Open data, linked data, semantic web, Nobel Prize, politician, European Parliament.
\end{IEEEkeywords}}


% make the title area
\maketitle

\IEEEdisplaynontitleabstractindextext

\IEEEpeerreviewmaketitle

\IEEEPARstart{S}{ince} 1901, every year there are 5 Nobel Prizes awarded to people all over the world. Each prize is for a specific field namely: Physics, Chemistry, Physiology or Medicine, Literature and Peace. In 1968 the Nobel Prize in Economic Sciences was added to this list and first awarded in 1969.
These prizes are rewarded in memory of Alfred Nobel \cite{nobelNobel}.
He was a chemist, engineer and inventor who during his lifetime made a fortune because of his large amount of inventions. His last will stated that his fortune be used to create a series of prizes for those who confer the "greatest benefit on mankind" \cite{wikiNobel}. 
Some of these prize have been received by politicians. Notable ones are: Nelson Mandela (Nobel Peace Prize 1993), Barack Obama (Nobel Peace Prize 2009) and Winston Churchill (Nobel Prize in Literature 1953) \cite{nobelList}.

We are interested in finding a model that is able to predict the probability of a politician to win a Nobel Prize.


\hfill \today

\subsection{Research question}
\subsubsection{Motivation}
There is a whole process of nominations and selection before the Nobel Prizes are handed out. This is a complex process that takes some time \cite{nobelNomination}.
Because of the non-triviality of who will win the prize, it would be interesting to have a model that is able to predict how likely a person is to win the prize based on his characteristics. We are mainly interested how this would apply to politicians. 
\subsubsection{Research question}
\par For this reason, the question which this paper attempts to answer is:
\begin{center}
\textit{"Which European politicians have a high chance of receiving a Nobel Prize?"}	
\end{center}
In this context, European politicians are those who settle in the European Parliament. With \textit{a high chance} we mean the probability that someone would get awarded a Nobel Prize during his lifetime.

\subsection{Structure of this paper}
After this introduction we will elaborate on our methodology. The first section explains how we tackled the problem. The following sections will elaborate on each of these steps. In Section~\ref{sec:data} we discuss the data needed to answer our question and where we get it. 
Section~\ref{sec:analysis} focuses on data analysis. This covers some statistics to assess the quality of our data and introduces the learned model. We then show the results of applying the model in Section~\ref{sec:results}. To conclude this all we make a conclusion in section 5. Finally, we suggest some things that can be interesting for future research.

\input{sections/methodology}
\input{sections/data}
\input{sections/analysis}

\section{Results}
\label{sec:results}

\section{Conclusion}

\section{Future work}

We could broaden our training dataset by not only including people that won a Nobel Prize, but also gathering people who were ever nominated for one. They are not available on the LoD from Nobelprize.org but can be found on the website itself\cite{nominated}.
Our dataset could maybe also be enlarged with individuals who nominate other candidates. These people might be interesting because they are usually also influencial in the field of study from their proposed candidate.


\todo[inline]{Nog iets extra?}

% use section* for acknowledgment
\ifCLASSOPTIONcompsoc
  % The Computer Society usually uses the plural form
  \section*{Acknowledgments}
  We would like to thank our supervisors professor Bettina Berendt and Sebastijan Dumancic for their enthousiasm and support.
\else
  % regular IEEE prefers the singular form
  \section*{Acknowledgment}
\fi

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\printbibliography


\appendices
%\onecolumn

\clearpage
\input{appendices/productivity}

\clearpage
\input{appendices/googlescholar}

\clearpage
\input{appendices/sparql}


% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
%\input{appendices/queries}


%\section{Source code}
%Appendix two text goes here.
%\lstinputlisting[language=Java, caption=Opdracht 1]{../src/Main.java}
%\lstinputlisting[language=Java, caption=NobelPrice]{../src/NobelPrize.java}
%\lstinputlisting[language=Perl, caption=getRankings.pl]{../scripts/getRankings.pl}

\end{document}

