\documentclass[nonav,sleutel]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\title{Politicians and Nobel Prizes}
\date[ISPN '80]{Prof. Dr. Bettina Berendt\\ Knowledge \& the Web 2015-2016}
\author{Katrien Laenen \and Gust Verbruggen \and Ward Schodts}

\usetheme{kuleuvenstijl}




\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\titlepage
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[noframenumbering]
\frametitle{Outline} 
  \tableofcontents[hideallsubsections
  ]

\end{frame}

\AtBeginSection[]
{
 \begin{frame}<beamer>
 \frametitle{Outline}
 \tableofcontents[hideothersubsections,currentsection]
 \end{frame}
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\subsection{Some history}
\begin{frame}
\frametitle{Introduction} 
\framesubtitle{Some history} 
\begin{theorem}
There is no largest prime number. \end{theorem} 
\begin{enumerate} 
\item<1-| alert@1> Suppose $p$ were the largest prime number. 
\item<2-> Let $q$ be the product of the first $p$ numbers. 
\item<3-> Then $q+1$ is not divisible by any of them. 
\item<1-> But $q + 1$ is greater than $1$, thus divisible by some prime
number not in the first $p$ numbers.
\end{enumerate}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The research question}
\begin{frame}
\frametitle{Our research question} 

\textit{\textbf{\Large ``Which European politicians have a high chance of
receiving a Nobel Prize?''}}


\end{frame}

\section{Methodology}
\begin{frame}{Blocks}
\begin{block}{Block title}
Block body.
qsdfdqsf\\
qdsqf\\
\end{block}
\begin{example}
For clarity:
\begin{itemize}
	\item[$\rightarrow$] first bullet point \ldots
	\item[$\rightarrow$] second bullet  point \ldots
\end{itemize}
\end{example}
\end{frame}

\section{Data}

\section{Data analysis}

\subsection{Outlier detection}


\section{Results}

\section{Conclusion}

\begin{frame}
\begin{center}
\Large{Thanks for listening}\\
Any questions?
\end{center}

\end{frame}

\begin{frame}
\frametitle{Our questions}
\begin{enumerate}
\item 
\end{enumerate}
\end{frame}

\end{document}