\documentclass[11pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{url}
\usepackage{hyperref}
\author{
  Katrien Laenen\\
  \and
  Gust Verbruggen\\
  \and
  Ward Schodts
}
\title{Knowledge \& the web: exercise session 4}
\begin{document}
\maketitle
\section{Interesting knowledge bases}
\begin{enumerate}

\item Musicbrainz
\item \url{data.nobelprize.org}
\item \url{http://datahub.io/dataset/zdb}
\item \url{www.linkedtv.eu}

\end{enumerate}

\section{Interesting questions}

All questions involve speakers from the ToE knowledge base. By combining these with other knowledge bases, we can infer other interesting properties about them. 


\subsection{How many and which European Parliament members were involved in criminal activities?}

DBpedia contains information on criminal activities for people.

\subsection{Which politicians have a good chance of receiving a Nobel Prize?}

The nobelprize knowledge base holds information on Nobel Prize winners. By searching for similarities (through for example DBpedia) between Nobel Prize winners and politicians, we can maybe find out which politicians have a (high) chance of receiving a Nobel Prize.

\subsection{Which song came out on the birthday of a specific politician?}

ToE contains birth dates for speakers, so we only have to combine it with artist information from musicbrainz to find our answer.

\subsection{Which politicians have a high chance of being murdered?}

Freebase contains the cause of death for deceased people, so yet again by searching for similarities with the European Parliament speakers, we can see who has a high chance of being murdered.

\subsection{Which European Parliament speakers have published bibliographic material?}

The ZDB knowledge base contains information about bibliographic resources in many languages, chances are therefore high that at least one of the European Parliament speakers has published such material.

\subsection{Which politicians have the most tv appearances?}

The LinkedTV project aims to annotate media fragments with metadata, such as \emph{faces} that appear in them. We would like to find out if one of our speakers has made such television appearance.

\end{document}
